Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-15 manuscript.tex
Added source to manuscript
done researching hurricanes; starting code

\documentclass{article}
% \usepackage[margin=2.5cm]{geometry}
\usepackage[margin=2.5cm, headheight=0pt, headsep=1cm]{geometry}
\usepackage{enumerate, fancyhdr, graphicx, amsmath, nth}
\usepackage[binary-units=true]{siunitx}

\title{Exit Strategy}
\author{Paul Chesnais, Antoine Pourchet and Ryan Vogan}
\date{\today}

\pagestyle{fancy}
\fancyhead{}
\lhead{Chesnais, Pourchet, Vogan}
\chead{Exit Strategy}
\rhead{\today}
\fancyfoot{}
\rfoot{\thepage}
\lfoot{\includegraphics[height=20pt]{Logo}}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

@@

\begin{thebibliography}{9}
  \bibitem{pmc}
    \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
\end{thebibliography}

>>>>

\documentclass[titlepage]{article}
% \usepackage[margin=2.5cm]{geometry}
\usepackage[margin=2.5cm, headheight=0pt, headsep=1cm]{geometry}
\usepackage{enumerate, fancyhdr, graphicx, amsmath, nth}
\usepackage[binary-units=true]{siunitx}

\title{Hurricane Evacuation Strategies for the State of Mississippi}
\author{A submission for the 2015 Cornell Mathematical Contest in Modeling \\ Prepared by Paul Chesnais, Antoine Pourchet and Ryan Vogan}
\date{November 16, 2015}

\pagestyle{fancy}
\fancyhead{}
\lhead{Chesnais, Pourchet, Vogan}
\chead{Hurricane Evacuation Strategies}
\rhead{\today}
\fancyfoot{}
\rfoot{\thepage}
\lfoot{\includegraphics[height=20pt]{Logo}}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

@@

\begin{thebibliography}{9}
  \bibitem{pmc}
    \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
  \bibitem{ms_highways}
    \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
\end{thebibliography}
